A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-16 papers/publication/paper-pollard.tex
Addded a bit to references, made plot.R better.

The complexity of Graphalytics obfuscates the true behavior of the program. By default, Graphalytics generates an HTML report listing the runtimes for each dataset and each algorithm in seconds. For example, one run of a single source shortest paths algorithm took 5.6 seconds. However, perusing the log files reveals a more complete picture: of these 5.96 seconds, 0.21 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures. Furthermore, data such as the number of iterations run for PageRank is not easily available using Graphalytics.
%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
% The full logs:
%Finished setting ids, time: 0.157009
%Starting sort
%Finished sort, time: 1.39571
%Finished setting edge pointers, time: 0.000133
%Starting build_dcsc
%Finished build_dcsc, time: 0.235948
%Finished setting ids, time: 0.154693
%Starting sort
%Finished sort, time: 1.75676
%Finished setting edge pointers, time: 0.000142
%Starting build_dcsc
%Finished build_dcsc, time: 0.238386
%Completed reading A from memory in 4.089144 seconds.
%Completed reading A from file in 5.114708 seconds
%Completed 19 iterations
%Timing results:
%- load graph: 5.11472 sec
%- initialize engine: 2.88486e-05 sec
%- run algorithm: 0.212451 sec
%- print output: 0.0799532 sec
%- deinitialize engine: 2.88486e-05 sec
%17:29:05.575 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 5955 ms.

@@

>>>>

The complexity of Graphalytics obfuscates the true behavior of the program. By default, Graphalytics generates an HTML report listing the runtimes for each dataset and each algorithm in seconds. For example, one run of a single source shortest paths algorithm took 5.6 seconds. However, perusing the log files reveals a more complete picture: of these 5.96 seconds, 0.21 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures. Furthermore, data such as the number of iterations run for PageRank are not easily available using Graphalytics.
%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
% The full logs:
%Finished setting ids, time: 0.157009
%Starting sort
%Finished sort, time: 1.39571
%Finished setting edge pointers, time: 0.000133
%Starting build_dcsc
%Finished build_dcsc, time: 0.235948
%Finished setting ids, time: 0.154693
%Starting sort
%Finished sort, time: 1.75676
%Finished setting edge pointers, time: 0.000142
%Starting build_dcsc
%Finished build_dcsc, time: 0.238386
%Completed reading A from memory in 4.089144 seconds.
%Completed reading A from file in 5.114708 seconds
%Completed 19 iterations
%Timing results:
%- load graph: 5.11472 sec
%- initialize engine: 2.88486e-05 sec
%- run algorithm: 0.212451 sec
%- print output: 0.0799532 sec
%- deinitialize engine: 2.88486e-05 sec
%17:29:05.575 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 5955 ms.

@@

Other related work includes that of \cite{Satish:2014:NavigatingGraph}, which analyzes performance of several systems on datasets on the order of $30$ billion edges and \cite{Lu:2014:ExperimentalEval} which uses six real-world datasets and focuses on the vertex-centric programming model.
